Reading Notes

### 2020-07-23 reading-notes.tex
reading/writing for the day
read paper about how forcefields fare when evaluating h-bonding and pistacking

TraPPE\cite{Maerzke2011}
it is generally assumed that coarse-grain potentials are not transferrable to different systems or state points (T and P). This model tries to fix that. uses IBI for bonded interactions and parameterize nonbonded interaction by fitting to vapor-liquid coexistence curves. parameters yield accurate vapor-liquid equilibria, first RDF peak, and coordination number for the solvation shell.
PMF represents enemble average free energy of FG model therefore it is limited to the same thermodynamic conditions. But the CG potential can also be viewed as an effective potential that is able to represent the interaction over wider range of condition--like how LJ represents pair and many-body interactions. Transferrable potentials may sacrifice accuracy at a specific potential.
IBI matches the shape but not the depth of the potential. structure of a liquid is mostly determined by repulsive interactions. Ref 17 was able to recover correct potential (after 1000 iter!) even though rdf appeared converged after 10(!!). adding pressure or energy to the iterative scheme sped up the convergence. Pressure and energy corrections can improve performance. 
Force matching does not rely on ensemble averaged property and has sounds statistical mechanics basis. variational.
MARTINI uses shifted LJ and params were fit to free energies of vaporization/hydration/partitioning between water/organics phases at 300K. 
the params of these ffs may be transferrable to different molecules (eg. alkyl chain can be used in different molecules) but not across different state points.
TraPPE-CG - minimize number of atom types. parameterized to TraPPE UA based on saturated vapor/liquid densities, internal energy of vaporization, transfer free energies are given greatest weight, rdf also considered. tabulated potential spaced by 0.05 A with linear interpolation. shifted so that U=0 at rcut=14A

@@

\cite{Shelley2001}
CG model for phospholipids. parameterized to mimic structural properties--which ones? they were fit to bond distributions (algorithm sounds like IBI but they don't say IBI... anyway it's iterative based on Boltzmann inverse of RDF)
reproduces structure of bilayer--property that was not directly fit. The initial configuration was random. 
how do they verify that it reproduces the bilayer? rdfs, density maps, also snapshots.

and read this: \cite{Chakraborty2018a}

@@

\bibliography{library}
\bibliographystyle{ieeetr}
\end{document}

>>>>

TraPPE\cite{Maerzke2011}

It is generally assumed that coarse-grain potentials are not transferrable to different systems or state points (T and P). This model tries to fix that. uses IBI for bonded interactions and parameterize nonbonded interaction by fitting to vapor-liquid coexistence curves. parameters yield accurate vapor-liquid equilibria, first RDF peak, and coordination number for the solvation shell.

PMF represents enemble average free energy of FG model therefore it is limited to the same thermodynamic conditions. But the CG potential can also be viewed as an effective potential that is able to represent the interaction over wider range of condition--like how LJ represents pair and many-body interactions. Transferrable potentials may sacrifice accuracy at a specific potential.
IBI matches the shape but not the depth of the potential. structure of a liquid is mostly determined by repulsive interactions. Ref 17 was able to recover correct potential (after 1000 iter!) even though rdf appeared converged after 10(!!). adding pressure or energy to the iterative scheme sped up the convergence. Pressure and energy corrections can improve performance. 
Force matching does not rely on ensemble averaged property and has sounds statistical mechanics basis. variational.
MARTINI uses shifted LJ and params were fit to free energies of vaporization/hydration/partitioning between water/organics phases at 300K. 
the params of these ffs may be transferrable to different molecules (eg. alkyl chain can be used in different molecules) but not across different state points.
TraPPE-CG - minimize number of atom types. parameterized to TraPPE UA based on saturated vapor/liquid densities, internal energy of vaporization, transfer free energies are given greatest weight, rdf also considered. tabulated potential spaced by 0.05 A with linear interpolation. shifted so that U=0 at rcut=14A

@@

\cite{Shelley2001}√
CG model for phospholipids. parameterized to mimic structural properties--which ones? they were fit to bond distributions (algorithm sounds like IBI but they don't say IBI... anyway it's iterative based on Boltzmann inverse of RDF)
reproduces structure of bilayer--property that was not directly fit. The initial configuration was random. 
how do they verify that it reproduces the bilayer? rdfs, density maps, also snapshots.

and read this: \cite{Chakraborty2018a} √

@@

\cite{Paton2009a}

comparing forcefields to DFT specifically seeing if force field can accurately represent hydrogen bonding, pi-stacking, and other non-bonded interactions.
dispersion forces are very important for DNA stabilization
this paper looks at small molecule dimers which are relelvant to biomolecules in the gas phase (e.g., adenine/thymine dna base pair)
the break apart the molecules based on what is the dominant interaction: h-bonded, dispersion, or mixed.
All FFs underestimated hydrogen bonding but overall structures/energies are not bad.

\cite{Paul1995a}
\cite{Yang2006a}
\cite{McCoy1998a}
\bibliography{library}
\bibliographystyle{ieeetr}
\end{document}
